\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\usepackage{mathptmx} % Times New Roman-like font


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\setlength{\footskip}{4.1pt}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Nur Amalia binti Jamaludin} \\ \vspace{-1pt}
    A motivated and dedicated individual seeking a dynamic role where I can leverage my skills and expertise to drive innovation and contribute meaningfully to the organization's success and growth.\\ \vspace{2pt}
    \small
    \href{mailto:namaliaj@umich.edu}{\raisebox{-0.2\height}\faEnvelope\ \underline{namaliaj@umich.edu}} ~
    \href{https://github.com/amaliajamaludin}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/amaliajamaludin}} ~
    \href{https://www.linkedin.com/in/amaliajamaludin/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/amaliajamaludin/}} \\
    \vspace{-8pt}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\small
\resumeSubHeadingListStart
\resumeSubheading
{University of Michigan-Dearborn}
{Dearborn, Michigan}
{Bachelor of Science in \textbf{Software Engineering}} {Concentration: \textbf{Web Development}} \vspace{2pt}
{\small\break{\textit{ Minor in \textbf{Economics}}}}
\break{GPA: \textbf{3.97}}
\hfill
{\textbf{Aug 2021 -- Apr 2025}}
\vspace{-5pt}
  \resumeSubHeadingListEnd
%-----------PROJECT-----------  
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

% Project 1: South Asian Multilingual Dictionary
\resumeProjectHeading
    {\textbf{South Asian Multilingual Dictionary} $|$ Team Lead, Backend Developer, DevOps Engineer }{Sept 2024 - Present}\vspace{-5pt}
    {\small \break\emph{React, Express, Node.js, Google OAuth, MiDatabase, Shibboleth, UMich Container Service}}\vspace{-5pt}
    \resumeItemListStart
        \resumeItem{Leading the project development, coordinating with clients to gather requirements and ensure project alignment.}
        \resumeItem{Utilizing the MERN stack and Google OAuth for app development, integrating Shibboleth for Single Sign-On (SSO).}
        \resumeItem{Managing DevOps practices and backend development using MiDatabase for efficient data storage.}
        \resumeItem{Documenting the software project management and applying Agile methodologies to oversee project sprints.}
    \resumeItemListEnd
    \vspace{-10pt}

% Project 2: CityWatch
\resumeProjectHeading
    {\textbf{CityWatch} $|$ Frontend Developer, UI/UX Designer }{Sept 2024 - Present}\vspace{-5pt}
    {\small \break\emph{Figma, MySQL, PhpMyAdmin, HTML, CSS, JavaScript, Django, Flask, Python, Jira}} \vspace{-5pt}
    \resumeItemListStart
        \resumeItem{Designed the UI/UX experience using Figma, focusing on user-friendly interfaces and navigation.}
        \resumeItem{Developing the frontend with HTML, CSS, and JavaScript and using MySQL as the database via PhpMyAdmin.}
        \resumeItem{Building the backend services using Flask and Django, ensuring smooth data exchange between frontend and database.}
        \resumeItem{Applying Agile methodologies to manage frontend tasks and design iterations, using Jira to track progress.}
        \resumeItem{Documenting frontend design choices and team management.}
    \resumeItemListEnd  
    \vspace{-10pt}

% Project 3: TravelShare
\resumeProjectHeading
    {\textbf{TravelShare} $|$ Frontend Developer, UI/UX Designer}{Jan 2024 - Apr 2024}\vspace{-5pt}
    {\small \break \emph{MongoDB, React, Express, Node.js, RESTful APIs}}\vspace{-5pt}
    \resumeItemListStart
    \resumeItem{Developed a travel-sharing platform with the MERN stack, using RESTful APIs for real-time itinerary collaboration.}
    \resumeItem{Designed a user-friendly frontend UI/UX for seamless navigation of planning features.}
    \resumeItem{Implemented route planning and itinerary sharing, synchronizing data via RESTful APIs.}
    \resumeItem{Applied Agile methodologies to manage collaboration and sprints, documenting frontend and backend structures.}
\resumeItemListEnd
    \vspace{-5pt}
\resumeSubHeadingListEnd 
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\footnotesize
\resumeSubHeadingListStart
  \item{
    \textbf{Programming Languages:} Python, JavaScript, C++, SQL, Java, PHP
  }
  \item{
    \textbf{Web Development:} HTML, CSS, React, Node.js, Figma
  }
  \item{
    \textbf{Data Analysis \& Visualization:} Pandas, NumPy, Matplotlib, Seaborn, Stata
  }
  \item{
    \textbf{Databases:} MySQL, MongoDB, PostgreSQL
  }
  \item{
    \textbf{Technologies:} Git/GitHub, Docker, Eclipse
  }
  \item{
    \textbf{Methodologies:} Agile, Scrum
  }
  \item{
    \textbf{Highlighted Skills:} Software Engineering, Project Management, Strong Documentation, Technical Design, Collaboration, Debugging
  }
\resumeSubHeadingListEnd
\vspace{-16pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    \footnotesize
    %resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Design Seminar Software Engineering
                \item Database Management System
                \item Information System
                \item Computer Network and Disc Processor
                \item Software Engineering I \& II
                \item Artificial Intelligence
                \item Software Architecture \& Design Pattern
                \item Data Structure \& Algorithm
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------INVOLVEMENT---------------
\section{Fellowship \& Awards Certificate}
\footnotesize
    \resumeSubHeadingListStart 
        \resumeSubheading{Summer Undergraduate Research Experience (SURE)}{May 2024 - Present}{Research Fellow}{University of Michigan-Dearborn}
        \vspace{1pt}
            \resumeItemListStart
                \resumeItem{Estimated the effect of retail health clinics on wait times 
                using Stata.}
                \resumeItem{Collaborated on data analysis and presented at the SURE Showcase.}\vspace{3pt}
            \resumeItemListEnd

        \resumeSubheading{Introduction to Data Science in Python}{Oct 2024}{Coursera Certificate}{Coursera}
        \vspace{1pt}
            \resumeItemListStart
                \resumeItem{Completed Python-based data science coursework on data wrangling and analysis.}\vspace{3pt}
            \resumeItemListEnd
        
        \resumeSubheading{James B. Angell Scholar}{Mar 2023}{University of Michigan-Dearborn}{University of Michigan-Dearborn}
        \vspace{3pt}
            \resumeItemListStart
                \resumeItem{Awarded for earning straight A's across two or more terms with at least 14 credit hours per term.}\vspace{3pt}
            \resumeItemListEnd

        \resumeSubheading{University Honors}{Dec 2021}{University of Michigan-Dearborn}{University of Michigan-Dearborn}
        \vspace{1pt}
            \resumeItemListStart
                \resumeItem{Recognized for achieving a GPA of 3.50+ and completing 14 credit hours.}\vspace{3pt}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\end{document}
